Glyph-maps for Visually Exploring Temporal Patterns in Climate Data and Models

### 2012-03-03 revision/paper.tex
Add colour package to stop complaints
Update plots and add legend to ref frames section

\documentclass[oneside]{article}
\usepackage{fullpage}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{{images/}}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage[format=plain,font=small]{caption}
\usepackage[small]{titlesec}
\usepackage[round,sectionbib]{natbib}
\usepackage{amstext}
\usepackage{setspace}
\bibliographystyle{plainnat}
\renewcommand\rmdefault{bch}
\linespread{1.07}

@@

  \caption{Glyph-maps of seasonal temperature patterns (averages for each month), using the data-expo data. Adding mid-range reference lines (left) and grid-cell reference boxes (right), makes it easier to see differences in glyph position, not just shape.}
  \label{fig:ref-basic}
\end{figure}

>>>>

\documentclass[oneside]{article}
\usepackage{fullpage}
\usepackage[pdftex]{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{{images/}}
\usepackage[dvipsnames,usenames]{color}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage[format=plain,font=small]{caption}
\usepackage[small]{titlesec}
\usepackage[round,sectionbib]{natbib}
\usepackage{amstext}
\usepackage{setspace}
\bibliographystyle{plainnat}
\renewcommand\rmdefault{bch}
\linespread{1.07}

@@

  \includegraphics[width=0.33\linewidth]{ref-legend}

  \caption{Glyph-maps of seasonal temperature patterns (averages for each month), using the data-expo data. Adding mid-range reference lines (top-left) and grid-cell reference boxes (top-right), makes it easier to see differences in glyph position, not just shape. (Bottom) Legend shows overall scales to aid interpretation.}
  \label{fig:ref-basic}
\end{figure}
